Between-dataset comparisons

### 2019-11-13 analysis/reports/compare_datasets.Rmd
dataset intersection report, increase bbs memory

for(i in 1:6) {

@@

@@

all_statevars <- all_statevars %>%
  filter(!singletons) %>%
  mutate(in_bbs = between(s0, all_extremes$min_s0[1], all_extremes$max_s0[1]) + between(n0, all_extremes$min_n0[1], all_extremes$max_n0[1]) == 2,
         in_fia = between(s0, all_extremes$min_s0[3], all_extremes$max_s0[3]) + between(n0, all_extremes$min_n0[3], all_extremes$max_n0[3]) == 2,
         in_gentry = between(s0, all_extremes$min_s0[5], all_extremes$max_s0[5]) + between(n0, all_extremes$min_n0[5], all_extremes$max_n0[5]) == 2,
         in_mcdb = between(s0, all_extremes$min_s0[7], all_extremes$max_s0[7]) + between(n0, all_extremes$min_n0[7], all_extremes$max_n0[7]) == 2,
         in_misc = between(s0, all_extremes$min_s0[9], all_extremes$max_s0[9]) + between(n0, all_extremes$min_n0[9], all_extremes$max_n0[9]) == 2,
         in_portal = between(s0, all_extremes$min_s0[11], all_extremes$max_s0[11]) + between(n0, all_extremes$min_n0[11], all_extremes$max_n0[11]) == 2) %>%
  mutate(total_in = in_bbs + in_fia + in_gentry + in_mcdb + in_misc + in_portal)

@@

>>>>

#datasets <- c("fia", "gentry", "mcdb", "misc_abund_short", "portal_plants")

for(i in 1:length(datasets)) {

@@

## Overall dataset spaces

```{r overall spaces}

overall <- ggplot(data = filter(all_statevars, !singletons), aes(x = s0, y = n0)) +
  geom_point(alpha = .3) +
  theme_bw() +
  facet_wrap(vars(dat), scales = "fixed")
overall
```

@@

all_statevars <- all_statevars %>%
  filter(!singletons) %>%
  mutate(
     in_bbs = between(s0, filter(all_extremes, dat == "bbs", singletons == F)$min_s0[1], filter(all_extremes, dat == "bbs", singletons == F)$max_s0[1]) + between(n0, filter(all_extremes, dat == "bbs", singletons == F)$min_n0[1], filter(all_extremes, dat == "bbs", singletons == F)$max_n0[1]) == 2,
    in_fia = between(s0, filter(all_extremes, dat == "fia", singletons == F)$min_s0[1], filter(all_extremes, dat == "fia", singletons == F)$max_s0[1]) + between(n0, filter(all_extremes, dat == "fia", singletons == F)$min_n0[1], filter(all_extremes, dat == "fia", singletons == F)$max_n0[1]) == 2,
    in_gentry = between(s0, filter(all_extremes, dat == "gentry", singletons == F)$min_s0[1], filter(all_extremes, dat == "gentry", singletons == F)$max_s0[1]) + between(n0, filter(all_extremes, dat == "gentry", singletons == F)$min_n0[1], filter(all_extremes, dat == "gentry", singletons == F)$max_n0[1]) == 2,
    in_mcdb = between(s0, filter(all_extremes, dat == "mcdb", singletons == F)$max_s0[1], filter(all_extremes, dat == "mcdb", singletons == F)$max_s0[1]) + between(n0, filter(all_extremes, dat == "mcdb", singletons == F)$min_n0[1], filter(all_extremes, dat == "mcdb", singletons == F)$max_n0[1]) == 2,
    in_misc = between(s0, filter(all_extremes, dat == "misc_abund_short", singletons == F)$max_s0[1], filter(all_extremes, dat == "misc_abund_short", singletons == F)$max_s0[1]) + between(n0, filter(all_extremes, dat == "misc_abund_short", singletons == F)$min_n0[1], filter(all_extremes, dat == "misc_abund_short", singletons == F)$max_n0[1]) == 2,
    in_portal = between(s0, filter(all_extremes, dat == "portal_plants", singletons == F)$max_s0[1], filter(all_extremes, dat == "portal_plants", singletons == F)$max_s0[1]) + between(n0, filter(all_extremes, dat == "portal_plants", singletons == F)$min_n0[1], filter(all_extremes, dat == "portal_plants", singletons == F)$max_n0[1]) == 2
    ) %>%
   mutate(total_in = in_bbs + in_fia + in_gentry + in_mcdb + in_misc + in_portal)
  # mutate(total_in =in_fia + in_gentry + in_mcdb + in_misc + in_portal)

@@

```{r intersection plot}

intersection_plot <- ggplot(data = filter(all_statevars, singletons == FALSE, total_in > 1), aes(x = s0, y = n0, color = as.factor(total_in))) +
  geom_point(alpha = .2) +
  theme_bw() +
  scale_color_viridis_d(option = "plasma", end = .9)
intersection_plot

```
I don't trust that occupancy. Here's another approach.

```{r new occupancy}

max_min_s0 = max(all_extremes$min_s0)
max_min_n0 = max(all_extremes$min_n0)

min_max_s0 = min(all_extremes$max_s0)
min_max_n0 = min(all_extremes$max_n0)

all_statevars_within <- all_statevars %>%
  filter(s0 > max_min_s0, s0 < min_max_s0, n0 > max_min_n0, n0 < min_max_n0, !singletons) %>%
  select(site, dat, s0, n0) %>%
  group_by(s0, n0) %>%
  mutate(ndats = length(unique(dat)),
         nsites = dplyr::n()) %>%
  ungroup()

new_occ <- ggplot(data = all_statevars_within, aes(x = s0,y = n0, color = as.factor(ndats))) +
  geom_point(alpha = .3) +
  scale_color_viridis_d(option = "plasma", end = .9, direction = -1) +
  theme_bw()
new_occ
```
